Assessing primitives performance\\ on multi-stage execution

### 2018-05-08 paper.tex
f

\paragraph{Final specification.} The final specification we productized last month takes two or three parameters. The third parameter, the order, is optional. If the third parameter is absent, the VM assumes the byte ordering (ASCII order) is the order to compare against. Therefore, the VM does not need to go through the indirection order array in the common case. The primitive answers a negative value if the first parameter is smaller than the second, 0 if they are equal, and a positive value if the first parameter is greater than the second one.
\cba{Maybe rewrite the last paragraph to make it clearer / more formal. - CF Java spec ? => This is critical, maybe in bold or in a box}

@@

\paragraph{Baseline: pure Smalltalk.}
: baseline
Smalltalk code on top of VM. Used as our baseline for benchmarks.

>>>>

\paragraph{Final specification.} The final specification we productized last month takes two or three parameters. The third parameter, the order, is optional. If the third parameter is absent, the VM assumes the byte ordering (ASCII order) is the order to compare against. Therefore, the VM does not need to go through the indirection order array in the common case. The primitive answers a negative integer, zero, or a positive integer as the first parameter is less than, equal to, or greater than the second parameter.

@@

\paragraph{Baseline: pure Smalltalk.}
\cba{Hum I believed that one should follow new specification and not old one ? With neg, 0 or pos value ?}
: baseline
Smalltalk code on top of VM. Used as our baseline for benchmarks.
